---
title: "Day 15: Point Mapping"
format: html
editor: source
---

```{r}
#| document: show
library(tidyverse)
library(echor)
echo_air_ca <- 
  echoAirGetFacilityInfo(p_st = "CA", 
                         qcolumns = "1,8,22,23,100") |>
  select(-SourceID)
```


# Create a map of ECHO facilities in California, colored by whether or not that facility has had a violation within the last three years

> Note that the CRS for "FacLong", "FacLat" in `echo_air_ca` is 4269. Remember that leaflet expects data in 4326.
> When I run a Google Search for California coordinates, I get the following (36.7783° N, 119.4179° W) Remember that South and West coordinates will be negative in our code. Google returns coordinates in WGS84 (CRS 4326). 


```{r}
library(sf)
library(leaflet)

#echo_air_ca_geo <- echo_air_ca |>
  #st_as_sf(_____) |>
  #st_transform(_____)

#violation_pal <- colorFactor(_____)

#leaflet() |>
  #setView() |>
  #addProviderTiles() |>
  #addCircleMarkers() |>
  #addLegend(_____)
```

