---
title: "Day 11: Problem Solving"
format: html
editor: source
---

```{r}
library(tidyverse)
library(lubridate)
hospitals <- read.csv("https://raw.githubusercontent.com/SDS-192-Intro/SDS-192-public-website/main/slides/datasets/Hospital_Cost_Report_2018.csv") |>
  mutate(
    Fiscal.Year.Begin.Date = ymd(Fiscal.Year.Begin.Date),
    Fiscal.Year.End.Date = ymd(Fiscal.Year.End.Date)) |>
  select(1:17, 22)

ma_county_pop <- read.csv("ma_county_2010_pop.csv") |>
  select(-X)
```

# Which city in the US has the most hospitals represented in this dataset?

> Hint: Remember that different states might have cities with the same name! 

```{r}
# Code here!
```

# In California, are there more rural or urban hospitals? Do rural or urban hospitals have more beds? Be sure to check for the number of hospitals with bed numbers missing. 

```{r}
# Code here!
```

# In Massachusetts, how many hospital beds per capita are there in each county?

```{r}
# Code here!
```

# Critical Access Hospitals (CCN.Facility Type: CAH) are expected to have 25 beds or fewer. In each state, which critical access hospital has the most number of beds, and how many beds does it have? Return a data frame listing the hospital's name, state, and number of beds, and order the data frame from most beds to least.

```{r}
# Code here!
```
